Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-01-30 revisionMemo/rev1.tex
MG and CD get shit done

		Insert great response.

@@

		Insert great response.

>>>>

		SM insert great response. 

@@

		We have edited P8 to read: Non-iid observations in relational data result from the fact that there is a complex structure underlying the dyadic events or processes we observe. We have also clarified the goals of the paper in the earlier sections. 
		\item Here we have clarified that our study does not address causal identification but instead focuses on providing unbiased estimates of covariates, calibrated confidence intervals that reduce inferential error, and improved predictive performance.  Though we understand these goals are not always central to every political scientists aim, we do believe they relate closely to the field of IR (as demonstrated by the studies we replicate) and a growing interest in forecasting and machine learning in Political Science. (CITE?)
		\item For part (a), we have clarified that our study does not address causal identification. We instead focuses on providing unbiased estimates of covariates, which improves inference for observational data.  
		\item As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions...relates to SM's to-do below.  
		\item Finally, we understand these goals are not always central political science research, but we believe that prediction is both a valuable metric to evaluate model performance as well as a goal for scholars in and of itself, as in \citet{people}.

### 2020-01-30 revisionMemo/rev2.tex
MG and CD get shit done

		Insert great response.

@@

		Insert great response.

@@

		TODO/CD: We agree with this suggestion. We have now emphasized the importance of developing theory in our discussion of the AME and Oracle comparison (p. X), as well as in the conclusion of our paper (p.Y).

@@

		TODO/CD: I think this comment and the above comment are essentially the same. We could even cite our JOP as an example of incorporating theory?  Perhaps other new-ish net paper as well?

@@

		TO DO/CD: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach (Max, more here on each?).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, they are beyond the scope of this paper at this time. (CD: Should we also mention something like 'in consultation with the editor, we believe they are beyond the scope....") 

>>>>

		CDMG: Flag for discussion. We brainstormed how to fit this into the simulation, but wouldn't simulating a W matrix be a bit arbitrary here? 

@@

		CDMG: Flag for discussion.

@@

		TO DO (CD): We agree with this suggestion. We have now emphasized the importance of developing theory in our discussion of the AME and Oracle comparison (p. X), as well as in the conclusion of our paper (p.Y). We agree that innovations in dependence modeling can and should speak to theoretical advancements that, like our model, take into account the important relational and interdependent nature of socio-political processes. JOP CITE.

@@

		TO DO (MG): We have added an additional paragraph on pg. 18 in our discussion of Reiter and Stam which reveals...For example in this case, the finding that countries in the middle east experience more violence might lead one to more carefully examine the effects of geography or natural resources on the intiation of conflict. 

@@

		TO DO/CD: We selected our cases based on a few criteria. We focus on studies that are explicitly about International Relations, were published in the last 10 years, and were published in a top ranking general political science outlet (for consistency in editorial standards and reviews, we also decided to focus on one journal, the APSR). We hope that these three criteria ensure that our paper is readable and interpretable to an applied audience. In addition, we selected studies that could help illustrate different key components of the AME approach such as random effects (Reiter and Stam), third-order dependencies (Weeks), precision of fixed effects estimates (Gibler).  While we agree with the reviewer that further replications would effectively demonstrate the benefits of the AME, they are beyond the scope of this paper at this time. (CD to SM: Should we also mention something like ``in consultation with the editor, we believe they are beyond the scope....") 
